---
title: "Isochrones"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```


# Appendix

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

Unlike the [Notes](https://scc-pi.github.io/notes/) site, the bulk of the rendering is done locally rather than via GitHub Actions. To some extent this is simpler, and it also works around where rendering needing to reference a local licensed installation of ArcGIS desktop. The site is setup as per the basic [GitHub Pages guidance](https://guides.github.com/features/pages). The rendering that isn't local is via a [Jekyll theme](https://docs.github.com/en/pages/setting-up-a-github-pages-site-with-jekyll/adding-a-theme-to-your-github-pages-site-using-jekyll).